### 2025-04-11 download-football-data.qmd
20250411 - add packages
20250411 - update data to remove infinite (implausible) values

@@

@@

nfl_actualStats_career_player_inclPost$fg_made_list[which(nfl_actualStats_career_player_inclPost$fg_made_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_missed_list[which(nfl_actualStats_career_player_inclPost$fg_missed_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_blocked_list[which(nfl_actualStats_career_player_inclPost$fg_blocked_list == "")] <- NA
nfl_actualStats_career_player_inclPost$gwfg_distance_list[which(nfl_actualStats_career_player_inclPost$gwfg_distance_list == "")] <- NA
```

@@

@@

@@

>>>>

We calculate historical actual season-by-season statistics in @sec-calculateActualSeasonalStats.

@@

We calculate historical actual career statistics in @sec-calculateActualCareerStats.

@@

nfl_actualStats_career_player_inclPost$fg_made_list[which(nfl_actualStats_career_player_inclPost$fg_made_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_missed_list[which(nfl_actualStats_career_player_inclPost$fg_missed_list == "")] <- NA
nfl_actualStats_career_player_inclPost$fg_blocked_list[which(nfl_actualStats_career_player_inclPost$fg_blocked_list == "")] <- NA
nfl_actualStats_career_player_inclPost$gwfg_distance_list[which(nfl_actualStats_career_player_inclPost$gwfg_distance_list == "")] <- NA

nfl_actualStats_career_player[sapply(nfl_actualStats_career_player, is.infinite)] <- NA
nfl_actualStats_career_player_inclPost[sapply(nfl_actualStats_career_player_inclPost, is.infinite)] <- NA
```

@@

```{r}
nfl_actualFantasyPoints_player_weekly_raw[sapply(nfl_actualFantasyPoints_player_weekly_raw, is.infinite)] <- NA
nfl_actualFantasyPoints_dst_weekly_raw[sapply(nfl_actualFantasyPoints_dst_weekly_raw, is.infinite)] <- NA
```

@@

```{r}
nfl_actualFantasyPoints_player_seasonal[sapply(nfl_actualFantasyPoints_player_seasonal, is.infinite)] <- NA
nfl_actualFantasyPoints_dst_seasonal[sapply(nfl_actualFantasyPoints_dst_seasonal, is.infinite)] <- NA
```

@@

Let's rearrange the data:
